---
title: "Week 3 Assignment"
author: "Faizan Younus"
date: "September 14, 2018"
output: html_document
---

3. Copy the introductory example. The vector name stores the extracted names.
R> name
[1] "Moe Szyslak" "Burns, C. Montgomery" "Rev. Timothy Lovejoy"
[4] "Ned Flanders" "Simpson, Homer" "Dr. Julius Hibbert"

(a) Use the tools of this chapter to rearrange the vector so that all elements conform to
    the standard first_name last_name.
(b) Construct a logical vector indicating whether a character has a title (i.e., Rev. and
    Dr.).
(c) Construct a logical vector indicating whether a character has a second name.

(a)

#Load library and data set
```{r}
library(stringr)
raw.data <- "555-1239Moe Szyslak(636) 555-0113Burns, C. Montgomery555-6542Rev. Timothy Lovejoy555 8904Ned Flanders636-555-3226Simpson, Homer5543642Dr. Julius Hibbert"
name <- unlist(str_extract_all(raw.data,"[[:alpha:]., ]{2,}"))
name
```

#Isolate names and remove titles.  
```{r}
N2 <- sub(" [A-z]{1}\\. "," ",name)
N3 <- sub("(\\w+),\\s(\\w+)","\\2 \\1", N2)
N4 <- sub("[A-z]{2,3}\\. ","",N3)
N4
```

# Creation of Data frame
```{r}
first_name <- str_extract(N4, "[[:alpha:]+]{2,}")
last_name <- str_extract(N4, "[[:space:]][[:alpha:]+]{2,}")
Simpsonnames <- data.frame(first_name, last_name)
Simpsonnames
```

(b)
```{r}
Title <- str_detect(name, "[[:alpha:]+]{2,3}[.]")
data.frame(Simpsonnames,Title)
```

(c)
```{r}
Secondname<- str_detect(name, "[A-Z]\\.")
data.frame(Simpsonnames,Secondname)
```


4. Describe the types of strings that conform to the following regular expressions and
construct an example that is matched by the regular expression.

(a) [0-9]+\\$
```{r}
PAttern1="[0-9]+\\$"
example1=c("123$345","zse$as")
str_detect(example1,PAttern1)
```
Numbers followed by $


(b) \\b[a-z]{1,4}\\b
```{r}
pattern2="\\b[a-z]{1,4}\\b"
example2=c("a","bc","def","ghij")
str_detect(example2,pattern2)
```
Words of 1 to 4 letters


(c) .*?\\.txt$
```{r}
pattern3=".*?\\.txt$"
example3=c(".txt","123.txt","abc.txt","a$b#1.txt")
str_detect(example3,pattern3)
```
String ending on .txt


(d) \\d{2}/\\d{2}/\\d{4}
```{r}
pattern4 = "\\d{2}/\\d{2}/\\d{4}"
example4=c("12/31/2017","01/01/2018")
str_detect(example4,pattern4)
```
Date format MM/DD/YYYY


(e) <(.+?)>.+?</\\1>
```{r}
pattern5="<(.+?)>.+?</\\1>"
example5=c("<h1>blah</h1>")
str_detect(example5,pattern5)
```
Characters between <> </>, Following pattern of HTML code. 

9. The following code hides a secret message. Crack it with R and regular expressions.
Hint: Some of the characters are more revealing than others! The code snippet is also
available in the materials at www.r-datacollection.com.

```{r}
SecretMessage <- "clcopCow1zmstc0d87wnkig7OvdicpNuggvhryn92Gjuwczi8hqrfpRxs5Aj5dwpn0TanwoUwisdij7Lj8kpf03AT5Idr3coc0bt7yczjatOaootj55t3Nj3ne6c4Sfek.r1w1YwwojigOd6vrfUrbz2.2bkAnbhzgv4R9i05zEcrop.wAgnb.SqoU65fPa1otfb7wEm24k6t3sR9zqe5fy89n6Nd5t9kc4fE905gmc4Rgxo5nhDk!gr"
Test1 <- unlist(str_extract_all(SecretMessage, "[[:upper:].]{1,}"))
Test2 <- str_replace_all(paste(Test1, collapse =''), "[.]", " ")
Test2
```


