---
title: "Week 5"
author: "Faizan Younus"
date: "September 28, 2018"
output: html_document
---


The chart above describes arrival delays for two airlines across five destinations. Your task is to:
(1) Create a .CSV file (or optionally, a MySQL database!) that includes all of the information above.
You're encouraged to use a "wide" structure similar to how the information appears above, so
that you can practice tidying and transformations as described below.
(2) Read the information from your .CSV file into R, and use tidyr and dplyr as needed to tidy
and transform your data.
(3) Perform analysis to compare the arrival delays for the two airlines.
(4) Your code should be in an R Markdown file, posted to rpubs.com, and should include narrative
descriptions of your data cleanup work, analysis, and conclusions. Please include in your
homework submission:
??? The URL to the .Rmd file in your GitHub repository. and
??? The URL for your rpubs.com web page

#Load Library
```{r}
library(tidyr)
library(dplyr)
```

#1)Create CSV of Data
```{r setup, include=FALSE}
csv <- rbind(c("","", "Los Angeles", "Phoenix", "San Diego", "San Francisco", "Seattle"),
  c("ALASKA", "On Time", 497, 221, 212, 503, 1841),
  c("ALASKA", "Delayed", 62, 12, 20, 102, 305),
  c("AM WEST", "On Time", 694, 4840, 383, 320, 201),
  c("AM WEST", "Delayed", 117, 415, 65, 129, 61))
```

#2)Loading data into R
```{r}
write.table(csv, file = "Week5FY.csv", sep = ",", col.names=F, row.names=F)
Rawwide_data <- read.csv(paste0("https://raw.githubusercontent.com/Fyoun123/Data607/master/Week%205/Week5FY.csv"),stringsAsFactors = F); Rawwide_data
```

Using Gather to create Key-Value Pairs:
```{r}
LongConversion <- gather(Rawwide_data,city,number,Los.Angeles:Seattle, factor_key = TRUE)
LongConversion
```

Renaming the Columns to be more approriate:
```{r}
colnames(LongConversion)[2] <- "Ontime/Delay"
colnames(LongConversion)[1] <- "Vendor"
```

Spread allows us to take two columns and create to columns, In this case breaking up out Ontime/Delay column in liue of the flight info. 
```{r}
LongConversion$Vendor <- factor(LongConversion$Vendor)
LongConversion2 <- spread(LongConversion,"Ontime/Delay","number")
LongConversion2
```

We use the Diplyr Fucniton Mutate to add new variables taht are functions of existing varaibles, in this case calcullating intitally the total number of flights. Group_by allows us to utilize our vendor as the driver when coupled with summarise. We can then simply divide the on time flights by the total flights. 

```{r}
Performace <- LongConversion2 %>% mutate(total = Delayed + `On Time`) %>% group_by(Vendor) %>% summarise(DT = sum(Delayed), OT = sum(`On Time`), Total = sum(total), OntimeP = round(OT/Total*100,digits = 2))
Performace
```

Same synthax as above, this time utizlizing the city as our groupping rather than our airline:

```{r}
Performace2 <- LongConversion2 %>% mutate(total = Delayed + `On Time`) %>% group_by(city) %>% summarise(DT = sum(Delayed), OT = sum(`On Time`), Total = sum(total), OntimeP = round(OT/Total*100,digits = 2))
Performace2
```

